Methods and Results

### 2022-05-02 ms.Rmd
Fixing up table rendering. Very odd, but it didn't like the 'pretty_table' chunk label. Or maybe needed a space between caption and tab.cap, but now working.

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: false
      reference_docx: template.docx
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```

@@

#### Meta-analysis
We analysed effect size data using the *metafor* @Metafor (vers `utils::packageVersion("metafor")`) package in R @R (vers `r paste0(R.Version()$major, ".", R.Version()$minor)`). To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological. We plotted overall meta-analytic means using the orchard plot package @NakaOrchard. Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study. To control for sources of non-independence, we included study and species-level random effects @Noble2017. We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl (vers `r utils::packageVersion("rotl")`. We used Grafen's method @Grafen to calculate branch lengths using the R package *ape* @ape (vers `r utils::packageVersion("ape")`). Overall, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`). As such, we did not include phylogeny in our models.

@@

When accounting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects. The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`)(Table \@ref(tab:pretty_table).

@@

```{r pretty_table, tab.cap = "Number of effect sizes, studies and species along with overall meta-analytic mean (average SMDH) and 95% confidence (CI) and prediction intervals (PI). Heterogeneity estimates and 95% CI's are also provided for study, trait, species and total heterogeneity (excluding sampling variance)"}

autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
ft <- flextable::flextable(table1)
ft %>%
  flextable::compose(part = "header", j = "n", value = as_paragraph("n", as_sub("effects"))) %>%
  flextable::compose(part = "header", j = "std", value = as_paragraph("n", as_sub("studies"))) %>%
  flextable::compose(part = "header", j = "spp", value = as_paragraph("n", as_sub("species"))) %>%
  flextable::compose(part = "header", j = "est", value = as_paragraph("Meta-analytic mean")) %>%
  flextable::compose(part = "header", j = "CI", value = as_paragraph("95% CI")) %>%
  flextable::compose(part = "header", j = "PI", value = as_paragraph("95% PI")) %>%
  flextable::compose(part = "header", j = "i2_stdy", value = as_paragraph("I", as_sup("2"), as_sub("study"))) %>%
  flextable::compose(part = "header", j = "i2_trait", value = as_paragraph("I", as_sup("2"), as_sub("trait"))) %>%
  flextable::compose(part = "header", j = "i2_species", value = as_paragraph("I", as_sup("2"), as_sub("species"))) %>%
  flextable::compose(part = "header", j = "i2_tot", value = as_paragraph("I", as_sup("2"), as_sub("total")))

>>>>

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: false
      tab_caption: yes
      fig_caption: yes
      reference_docx: template.docx
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```

@@

#### Meta-analysis
We analysed effect size data using the *metafor* @Metafor (vers `r utils::packageVersion("metafor")`) package in R @R (vers `r paste0(R.Version()$major, ".", R.Version()$minor)`). To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological. We plotted overall meta-analytic means using the orchard plot package @NakaOrchard. Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study. To control for sources of non-independence, we included study and species-level random effects @Noble2017. We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl (vers `r utils::packageVersion("rotl")`. We used Grafen's method @Grafen to calculate branch lengths using the R package *ape* @ape (vers `r utils::packageVersion("ape")`). Overall, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`). As such, we did not include phylogeny in our models.

@@

When accounting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects. The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`) (Table \@ref(tab:table1)).

@@

```{r table1, tab.cap = "Number of effect sizes, studies and species along with overall meta-analytic mean (average SMDH) and 95% confidence (CI) and prediction intervals (PI). Heterogeneity estimates and 95% CI's are also provided for study, trait, species and total heterogeneity (excluding sampling variance)"}

#autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
ft <- flextable::flextable(table1)
ft %>%
  flextable::compose(part = "header", j = "n", value = as_paragraph("n", as_sub("effects"))) %>%
  flextable::compose(part = "header", j = "std", value = as_paragraph("n", as_sub("studies"))) %>%
  flextable::compose(part = "header", j = "spp", value = as_paragraph("n", as_sub("species"))) %>%
  flextable::compose(part = "header", j = "est", value = as_paragraph("Meta-analytic mean")) %>%
  flextable::compose(part = "header", j = "CI", value = as_paragraph("95% CI")) %>%
  flextable::compose(part = "header", j = "PI", value = as_paragraph("95% PI")) %>%
  flextable::compose(part = "header", j = "i2_stdy", value = as_paragraph("I", as_sup("2"), as_sub("study"))) %>%
  flextable::compose(part = "header", j = "i2_trait", value = as_paragraph("I", as_sup("2"), as_sub("trait"))) %>%
  flextable::compose(part = "header", j = "i2_species", value = as_paragraph("I", as_sup("2"), as_sub("species"))) %>%
  flextable::compose(part = "header", j = "i2_tot", value = as_paragraph("I", as_sup("2"), as_sub("total"))) %>% 
  flextable::font(part = "header", font = "Times") %>% 
  flextable::font(part = "body", font = "Times") %>% 
  flextable::fit_to_width(max_width = 8)
